Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
Modify Appendix part

A sample is a subset of individuals or cases selected from the target population or sample frame to make inferences about that population [@fowler2013survey]. In the context of polls conducted by SurveyUSA, the sample refers to the survey respondents. Sample sizes vary across different SurveyUSA polls. For the 2024 U.S. presidential election cycle, SurveyUSA conducted 49 polls with sample sizes ranging from 507 to 2,330 registered or likely voters. The average sample size for these polls is approximately 1,045 households.

>>>>

A sample is a subset of individuals or cases selected from the target population or sample frame to make inferences about that population [@fowler2013survey]. In the context of polls conducted by SurveyUSA, the sample refers to the survey respondents. Sample sizes vary across different SurveyUSA polls. For the 2024 U.S. presidential election cycle, SurveyUSA conducted 49 polls with sample sizes ranging from 507 to 2,330 registered or likely voters. The average sample size for these polls is approximately 1,045 households.Selecting a representative sample size helps ensure the survey results can be generalized to the target population while maintaining statistical precision [@fowler2013survey].
